### 2016-08-11 ms/ms.tex
finished writing results and methods

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main topologies ---
modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. Modular community
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

>>>>

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.
